%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{multicol}
\usepackage{vwcol}  
\usepackage{amsmath}
\setlength{\columnsep}{1cm}
\usepackage{color}
\usepackage{hyperref}

\newcommand{\mybullet}[0]{\textcolor{mygray}{$\bullet$} }

\name{Jiri Roznovjak} % Your name
\address{\href{https://github.com/jiriroz}{github.com/jiriroz} \\ \href{https://www.linkedin.com/in/jroznovjak}{linkedin.com/in/jroznovjak}} % Your address
\address{\href{mailto:jiri.roznovjak@gmail.com}{jiri.roznovjak@gmail.com} \\ (508).667.6394 } % Your phone number and email
%original \address{(508)~$\cdot$~667~$\cdot$~6394 \\ jroznovjak@clarku.edu} 

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\color{jobcolor}
\begin{vwcol}[widths={0.45, 0.55}, indent=0pt, rule=0pt]
\textcolor{jobcolor}{\textbf{Clark University}}\\
\textcolor{mygray}{December 2017} \\
B.A. in Computer Science \& Mathematics \\
GPA: 3.8/4.0
\vspace{5 mm}
\\


\textcolor{jobcolor}{\textbf{Coursework}} \\ \mbox{Design and Analysis of Algorithms \mybullet Operating Systems}\\
Numerical Analysis \mybullet Stochastic Modeling \\
\mbox{Analysis of Programming Languages}\\ Probability and Statistics \mybullet Machine Learning


\end{vwcol}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

%------------------------------------------------

\begin{rSubsection}{Bloomberg L.P.}{February 2018 - present}{Software Engineer, Trading Systems Sell-Side - Transaction Blotters}{New York, NY}
\item Supporting "Blotters" which display trade data to clients - the heaviest-used functions in Trading Systems.
\item C++ backend insfrastructure with caching and messaging queues, JavaScript front-end.
\item Major contribution to onboarding and supporting 600+ buy-side clients onto new functinality.
\end{rSubsection}


%------------------------------------------------

\begin{rSubsection}{Bloomberg L.P.}{May 2017 - August 2017}{Software Engineering Intern, Trading Systems Money Market}{New York, NY}
\item Developed Python infrastructure for money market securities.
\item Developed parser for security offerings from government agencies.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Alden Research Laboratory, Inc.}{February 2016 - May 2017}{Software Development Intern}{Holden, MA}
\item Developed full-stack applications using PHP and JavaScript.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Academic Technology Services, Clark University}{September 2015 - December 2017}{Programming Intern}{Clark University, Worcester, MA}
\item Managed University's learning platform Moodle (PHP and JavaScript codebase)
\end{rSubsection}

%------------------------------------------------


\begin{rSubsection}{Clark University}{Summer 2015 and Summer 2016}{Research Assistant}{Boston, MA}
\item Created a mathematical model to analyze and predict mouse movements.
\item Paper \emph{Predictive Link Following for Accessible Web Browsing} accepted to ASSETS 2015 conference.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Department of Computer Science, Clark University}{September 2015 - December 2017}{Teaching Assistant}{Clark University, Worcester, MA}
\item TA for Algorithms and Programming Languages courses.
\end{rSubsection}

%------------------------------------------------

\end{rSection}

%----------------------------------------------------------------------------------------
%       HONORS & AWARDS
%----------------------------------------------------------------------------------------

\begin{rSection}{Honors \& Awards}

\color{jobcolor}
\begin{list}{$\boldsymbol{\cdot}$}{\leftmargin=0em}
\sectionskip
\itemsep -0.5em \vspace{-0.5em}
\item 2nd place in CCSCNE 2016 Programming Contest out of 38 teams.
\item Recipient of the Sherman Fairchild Summer Fellowship for undergraduate research.
\end{list}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\color{jobcolor}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
\textcolor{jobcolor}{Programming} & C++, Python, C, JavaScript, Bash \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
